Simulating an Isolated Dwarf Galaxy with Multi-Channel Feedback and Chemical Yields from Individual Stars

### 2018-08-20 main.tex
just fixed a few typos

\textbf{In addition, our model does not account for the stellar component of the radiation field that leads to H$^{-}$ photodetachment (E$_\gamma > 0.76$~eV), though we do account for the contribution from the UVB. We find that the H$_2$ fraction is more strongly dependent upon the Lyman-Werner radiation field, which is followed for each star, than the H$^{-}$ photodetachment rate. Our tests suggest that, by ignoring the stellar contribution to H$^{-}$ photodetachment, our results may represent upper limits on the H$_2$ mass. However, including this component will likely only make a substantial difference during periods of no star formation, when there are no massive stars with significant Lyman-Werner luminosities. We do not anticipate this to have a significant dynamical impact on our simulations, as is discussed in more detail in Appendix~\ref{appendix:H minus}}.

@@

\textbf{As discussed in Section~\ref{sec:molecular gas content}, H$_2$ formation is dominated by the gas-phase H$^{-}$ channel in our simulations. Accounting for the photodetachment of H$^{-}$ from the stellar radiation field, which may dominate over the UVB, ca be important for correctly modeling H$_2$ formation in low metallicity gas~\citep{Wolcott-Green2012}. To test the significance of this radiation in determining the final H$_2$ mass we run a grid of one-zone Grackle cooling models.\footnote{See the ``cooling\_cell.py'' example here for more details: https:\/\/grackle.readthedocs.io\/en\/grackle-3.1\/Python.html}  These runs iterate through the non-equillibrium chemistry and cooling solvers with a constant density (10~cm$^{-3}$) for 200~Myr. In Fig.~\ref{fig:Grackle grid} we plot the final H$_2$ mass fraction in these cells for variations over five orders of magnitude in the adopted H$^{-}$ photodetachment rate and the Lyman-Werner radiation background. As shown, the H$_2$ mass fraction is much more sensitive to the Lyman-Werner radiation field than the H$^-$ photodetachment rate. In effect, our simulations move left-to-right in this diagram (only) as stars form (right) or die (left). A complete model, including the stellar contribution to H$^{-}$ photodetachment, would move somewhat diagonally.}

>>>>

\textbf{In addition, our model does not account for the stellar component of the radiation field that leads to H$^{-}$ photodetachment ($E_\gamma > 0.76$~eV), though we do account for the contribution from the UVB. We find that the H$_2$ fraction is more strongly dependent upon the Lyman-Werner radiation field, which is followed for each star, than the H$^{-}$ photodetachment rate. Our tests suggest that, by ignoring the stellar contribution to H$^{-}$ photodetachment, our results may represent upper limits on the H$_2$ mass. However, including this component will likely only make a substantial difference during periods of no star formation, when there are no massive stars with significant Lyman-Werner luminosities. We do not anticipate this to have a significant dynamical impact on our simulations, as is discussed in more detail in Appendix~\ref{appendix:H minus}}.

@@

\textbf{As discussed in Section~\ref{sec:molecular gas content}, H$_2$ formation is dominated by the gas-phase H$^{-}$ channel in our simulations. Accounting for the photodetachment of H$^{-}$ from the stellar radiation field, which may dominate over the UVB, 
%mm ca 
    can 
be important for correctly modeling H$_2$ formation in low metallicity gas~\citep{Wolcott-Green2012}. To test the significance of this radiation in determining the final H$_2$ mass we run a grid of one-zone Grackle cooling models.\footnote{See the ``cooling\_cell.py'' example here for more details: https:\/\/grackle.readthedocs.io\/en\/grackle-3.1\/Python.html}  These runs iterate through the non-equillibrium chemistry and cooling solvers with a constant density (10~cm$^{-3}$) for 200~Myr. In Fig.~\ref{fig:Grackle grid} we plot the final H$_2$ mass fraction in these cells for variations over five orders of magnitude in the adopted H$^{-}$ photodetachment rate and the Lyman-Werner radiation background. As shown, the H$_2$ mass fraction is much more sensitive to the Lyman-Werner radiation field than the H$^-$ photodetachment rate. In effect, our simulations move left-to-right in this diagram (only) as stars form (right) or die (left). A complete model, including the stellar contribution to H$^{-}$ photodetachment, would move somewhat diagonally.}
